\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.

### 2016-10-20 ms.tex
small changes

\citep[e.g.][]{Showman2015}

@@

@@

\begin{Verbatim}[frame=single]
> spider_params.plot_planet()
\end{Verbatim}

Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date. If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.

@@

The performance tests were carried out on a single core of an Intel Core I5-3470 Processor.

@@

\subsection{Available models}\label{sec:ttof}

@@

@@

The only way to properly access the errors on the parameter values of interest, and test for degeneracies

@@

@@

\subsection{Results}\label{sec:results}

In table \ref{tab:results}

@@

\subsection{Discussion}\label{sec:Discussion}

>>>>

@@

A model instance is initialised by typing

\begin{Verbatim}[frame=single]
> spider_params = spiderman.ModelParams(MODEL)
\end{Verbatim}

Where MODEL is the chosen surface brightness distribution. The model parameters are then entered, and from there, generating a lightcurve to compare to data is as simple as entering

\begin{Verbatim}[frame=single]
> spider_params.lightcurve(t)
\end{Verbatim}

Where t an array of timepoints where the model is to be evaluated.

@@

Typing the command

\begin{Verbatim}[frame=single]
> spider_params.plot_planet(t)
\end{Verbatim}

Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date (t). If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.

@@

Figure \ref{fig:exec_time} shows the result of a performance test carried out on a single core of an Intel Core I5-3470 Processor. The length of time to produce a model with 1000 timepoints as a function of the number of segments of the model. The test shows that the execution time scales linearly with the number of segments in the model, which is expected, showing the overhead to run the model is very small. The precision required for typical usage can easily be reached using 16 or 25 segments, but larger numbers of segments can be used to produce better looking diagrams. The diagrams in this paper were generated with a 400 segment model.

@@

@@

As this effect is poorly understood, we run the fit both with and without planetary limb darkening.

@@

It is important to properly access the errors on the parameter values of interest, and test for degeneracies, so we run an MCMC analysis of the model fit. We use the \textsc{emcee}  affine invariant monte carlo implementation of \citet{emcee}

@@

The initial parameter positions are found with a least squares minimisation approach, and the walkers

@@

\subsection{Results and discussion}\label{sec:results}

The results of both runs are presented In table \ref{tab:results}. There is very little difference between the fitted parameters with and without limb darkening. The value of $T_n$ is lower by more than $3\sigma$ in the fit with planetary limb darkening

@@
